Biologically-Constrained Region Merging for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/4_results.tex
benchmark figure

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/voi-Kasthuri-Luigi-Test.png}
	\includegraphics[width=0.32\linewidth]{./figures/voi-FlyEM-Vol--1.png}
	\includegraphics[width=0.32\linewidth]{./figures/voi-FlyEM-Vol--2.png}
	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth. Lower scores are better. Our method improves the accuracy of the segmentation in all cases.}
	\label{fig:variation-of-information}
\end{figure*}

>>>>

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-Kasthuri-Luigi-Test.pdf}
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--1.pdf}
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--2.pdf}
	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth. Lower scores are better. Our method improves the accuracy of the segmentation in all cases.}
	\label{fig:variation-of-information}
\end{figure*}
